\LARGE \bf Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty [v 17]

### 2015-06-14 paper.tex
latest revision, changed figure and went over writing

In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and approach. 
A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time. Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  \cite{kehoe2012toward}\cite{kehoe2012estimating} in terms of finding a higher quality grasp faster.
However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
Fortunately, the probability of many successive samples being misleading approaches rapidly zero as the time horizon is increased.

>>>>

In this work, we proposed a multi-armed bandit approach to efficiently identify high-quality grasps under uncertainty in shape, pose, friction coefficient and approach. 
A key insight from our work is that exhaustively sampling each grasp is inefficient, and we found that a MAB approach gives priority to promising grasps and can reduce computational time. Initial results have shown MAB algorithms to outperform the methods of prior work, uniform allocation and iterative pruning  ~\cite{kehoe2012toward, kehoe2012estimating} in terms of finding a higher quality grasp faster.
However, as shown in Fig. \ref{fig:worst_case} there are some pathological cases that can mislead bandit algorithms to focus samples on the wrong grasps.
Fortunately, the probability of many successive samples being misleading approaches rapidly zero as the time horizon is increased.
